XXX

### 2012-03-25 paper/engNERwiki.tex
Paper structure.

The paper is structured as follows. XXX In section~\ref{sec:hun}, we show how the algorithm was adapted to Hungarian.

>>>>

The paper is structured as follows. In Section~\ref{sec:related} we give an overview of related works. We introduce our algorithm in Section~\ref{sec:create}, and show how it was adapted to Hungarian in Section~\ref{sec:hun}. The corpus format is described in Section~\ref{sec:data}. Section~\ref{sec:eval} contains evaluations and Section~\ref{sec:conclusion} our conclusions.
